Untitled

### 2020-07-21 manuscript/manuscript.Rmd
Finish analysis

It can be seen that this model has converged within approximately 10000 trees (Figure \@ref(fig:figconverge)). Thus, we will use this number of trees for subsequent analyses. We now apply pre-selection using the \texttt{preselect} function. This algorithm helps eliminate noise moderators by replicating the analysis 100-fold. Using \texttt{preselect_vars}, we retain only those moderators for which a 95% percentile interval of the variable importance metrics does not include zero (variable importance is counted as zero when a moderator is not included in the final step of the recursive algorithm).

```{r, eval = FALSE}
if(run_everything){
  # Model with 10000 trees for replication
mf_rep <- MetaForest(yi~.,
                        data = df_train,
                        whichweights = "random",
                        num.trees = 10000)
# Run recursive preselection, store results in object 'preselect'
preselected <- preselect(mf_rep,
                         replications = 100)
# Plot the results
plot(preselected)
# Retain only moderators with positive variable importance in more than
# 50% of replications
retain_mods <- preselect_vars(preselected, cutoff = .95)
yaml::write_yaml(retain_mods, "retain_mods.txt")
} else {
  retain_mods <- yaml::read_yaml("retain_mods.txt")
}

```{r figpreselect, eval=FALSE, fig.cap="Replicated variable importance for moderator pre-selection"}
# Plot the results
plot(preselected)
```

>>>>

It can be seen that this model has converged within approximately 10000 trees (Figure \@ref(fig:figconverge)). Thus, we will use this number of trees for subsequent analyses.
